---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**Grace Dai**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?

```{r my_plot}
covid_data_count |> 
  filter(race == "Total", state_name == "Florida" | state_name == "Massachusetts" | state_name == "New York") |> 
  ggplot(aes(x = date, y = Hosp, color = state_name)) + geom_point()
```

2. Are there any conclusions you can draw?
From mid October, New York has had a consistent high amount of COVID hospitalizations. Florida has had a positive liner growth of hospitalizations. Massachusetts has also had a positive liner growth, but it's slower than Florida. Overall, Florida's growth in hospitalizations has been the most out of the three states.

3. What were you not able to do due to not having the R knowledge?
I want to show a line of best line for each state to show the slopes.

4. What other data would be useful to better understand this data?
It would be useful if we had data from further into the year and the amount of vaccinations carried out for each state, so we could see if that effects the amount of hospitalizations. I would also want data on hospitalizations per capita to take into account state population.
